### 2018-12-10 Paper/revision/source_files/abstract.tex
..

\section*{Abstract}
Surrogate modeling has become a critical component of scientific computing
in situations involving expensive model evaluations. However, training a
surrogate model can be remarkably challenging and even computationally
prohibitive in the case of intensive simulations and large-dimensional
systems.
We develop a systematic approach for surrogate model
construction in reduced input parameter spaces.
%using derivative-based global sensitivity measures~(DGSMs)~\cite{Sobol:2010}. 
%
A sparse set of model evaluations in the original input space is used to  
approximate derivative based global sensitivity measures (DGSMs) 
for individual uncertain inputs of the model.
An iterative screening procedure is developed that exploits DGSM estimates in
order to identify the \emph{unimportant} inputs. The screening procedure forms
an integral part of an overall framework for adaptive construction of a
surrogate in the reduced space. The framework is tested for computational
efficiency through an initial implementation in simple test cases such as the
classic Borehole function, and a semilinear elliptic PDE with a random source
function. 
%Motivated by these experiences, the framework is fully implemented to
The framework is then deployed for a realistic application from chemical
kinetics, where we study the ignition delay in an H$_2$/O$_2$ reaction
mechanism with 19 uncertain rate constants.  It is observed that significant
computational gains can be attained by constructing accurate low-dimensional
surrogates using the proposed framework.
\vspace{2mm}

>>>>

\section*{Abstract}
Surrogate modeling has become a critical component of scientific computing
in situations involving expensive model evaluations. However, training a
surrogate model can be remarkably challenging and even computationally
prohibitive in the case of intensive simulations and large-dimensional
systems.
We develop a systematic approach for surrogate model
construction in reduced input parameter spaces.
%using derivative-based global sensitivity measures~(DGSMs)~\cite{Sobol:2010}. 
%
A sparse set of model evaluations in the original input space is used to  
approximate derivative based global sensitivity measures (DGSMs) 
for individual uncertain inputs of the model.
An iterative screening procedure is developed that exploits DGSM estimates in
order to identify the \emph{unimportant} inputs. The screening procedure forms
an integral part of an overall framework for adaptive construction of a
surrogate in the reduced space. The framework is tested for computational
efficiency through an initial implementation in simple test cases such as the
classic Borehole function, and a semilinear elliptic PDE with a random source
function. 
%Motivated by these experiences, the framework is fully implemented to
The framework is then deployed for a realistic application from chemical
kinetics, where we study the ignition delay in an H$_2$/O$_2$ reaction
mechanism with 19 and 33 uncertain rate-controlling parameters.  
It is observed that significant
computational gains can be attained by constructing accurate low-dimensional
surrogates using the proposed framework.
\vspace{2mm}

### 2018-12-10 Paper/revision/source_files/app.tex
..

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996} and fuel cell 
applications~\cite{Loges:2008,Cosnier:2016}. \rebut{We begin by providing
the necessary background information for setting up the problem
in~\ref{sub:setup}. Results and discussion based on the implementation
of the proposed framework are provided in~\ref{sub:imp}. Finally, 
in~\ref{sub:cost}, we
provide a comparative analysis of the computational cost involved
in determining relative parameter importance using DGSMs and the
total-effect Sobol' index as the dimensionality increases from 19 to 33
for the present application.}

@@

A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
and in 3D for
the fuel-lean case. Figure~\ref{fig:err_samples_kinetics}~(left) illustrates a
comparison of convergence characteristics for the PCEs constructed in the
full-space and the reduced-space for the fuel-rich case. Note that the
plot is generated using the implementation of least angle regression (LAR)
for sparse PCEs in UQLab.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics}
   \includegraphics[width=0.44\textwidth]{./Figures/errL2_samples_kinetics}
\caption{Left: A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
number of model evaluations in the full-space (19D) and the reduced-space (4D)
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
the PCE constructed using 60 training points was found to be 1 and 3 in the 19D and the 4D cases respectively.
Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
for the PCEs constructed in 4D and 19D.}}
\label{fig:err_samples_kinetics}
\end{center}
\end{figure}
%
The leave-one-out cross validation error is observed to drop initially
and plateau with the increase in training points for the 19-dimensional
PCE. However, in the case of 4-dimensional PCE, the error exhibits a
monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
\rebut{Additionally, the
convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
Figure~\ref{fig:err_samples_kinetics}~(right) indicates that for the case of 10
samples, the 4D PCE is observed to be more accurate. However, the 19D PCE
is observed to be more accurate by an order of magnitude as the sample size
increases. Specifically, the 4D PCE was found to be accurate within 1.8$\%$ in the
fuel-rich case, and within 3.1$\%$ in the fuel-lean case. Therefore, the 4D PCE
is still observed to be reasonably accurate in this case. Moreover, its faster convergence
as mentioned earlier should help reduce computational effort associated with
surrogate model construction.}
Similar trends (not included) were observed in the fuel-lean case.

@@

\rebut{
\subsection{Comparative cost analysis: higher-dimensional setting}
\label{sub:cost}

@@

}

>>>>

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996} and fuel cell 
applications~\cite{Loges:2008,Cosnier:2016}. We begin by providing
the necessary background information for setting up the problem
in~\ref{sub:setup}. Results and discussion based on the implementation
of the proposed framework are provided in~\ref{sub:imp}. Finally, 
in~\ref{sub:cost}, we
provide a comparative analysis of the computational cost involved
in determining relative parameter importance using DGSMs and the
total-effect Sobol' index as the dimensionality increases from 19 to 33
for the present application.

@@

A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
and in 3D for
the fuel-lean case. Figure~\ref{fig:err_samples_kinetics}~(left) illustrates a
comparison of convergence characteristics for the PCEs constructed in the
full-space and the reduced-space for the fuel-rich case. Note that the
plot is generated using the implementation of least angle regression (LAR)
for sparse PCEs in UQLab.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics}
   \includegraphics[width=0.44\textwidth]{./Figures/errL2_samples_kinetics}
\caption{Left: A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
number of model evaluations in the full-space (19D) and the reduced-space (4D)
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. The degree of
the PCE constructed using 60 training points was found to be 1 and 3 in the 19D and the 4D cases respectively.
Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
for the PCEs constructed in 4D and 19D.}
\label{fig:err_samples_kinetics}
\end{center}
\end{figure}
%
The leave-one-out cross validation error is observed to drop initially
and plateau with the increase in training points for the 19-dimensional
PCE. However, in the case of 4-dimensional PCE, the error exhibits a
monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
Additionally, the
convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
Figure~\ref{fig:err_samples_kinetics}~(right) indicates that for the case of 10
samples, the 4D PCE is observed to be more accurate. However, the 19D PCE
is observed to be more accurate by an order of magnitude as the sample size
increases. Specifically, the 4D PCE was found to be accurate within 1.8$\%$ in the
fuel-rich case, and within 3.1$\%$ in the fuel-lean case. Therefore, the 4D PCE
is still observed to be reasonably accurate in this case. Moreover, its faster convergence
as mentioned earlier should help reduce computational effort associated with
surrogate model construction.
Similar trends (not included) were observed in the fuel-lean case.

@@

\subsection{Comparative cost analysis: higher-dimensional setting}
\label{sub:cost}

@@

### 2018-12-10 Paper/revision/source_files/bg.tex
..

Derivative-based global sensitivity analysis is performed by 
computing derivative based global sensitivity measures (DGSMs)~\cite{Sobol:2009} 
for each uncertain parameter in the model. 
Specifically, we consider the following DGSMs, 
\be
\mu_i = 
\mathbb{E}\left[\left(\frac{\partial \GG(\bm{\bm{\theta}})}{\partial \theta_i}\right)^{2}\right], \quad i = 1, \ldots, \Np.
\label{eq:mu}
\ee
Here $\mathbb{E}$ denotes expectation over the uncertain parameters.
Notice that this formulation assumes that the function $\GG$ is differentiable
with respect to $\theta_i$, $i = 1, \ldots, \Np$.

@@

Consider the total 
Sobol' sensitivity index~\cite{Sobol:2001},
\be
\mathcal{T}(\theta_i) = 1 - 
\frac{\mathbb{V}[\mathbb{E}(\GG|\bm{\theta}_{\sim i})]}{\mathbb{V}(\GG)},
\label{eq:total}
\ee
where $\bm{\theta}_{\sim i}$ is the random vector $\bm\theta$ with $i$th component removed, 
and $\mathbb{V}$ denotes the variance. The total Sobol' index quantifies the total contribution 
of $\theta_i$ to variance of the model $\GG$. Components of $\bm\theta$ with small 
total Sobol' index can be considered inessential and can be fixed at nominal values. However, 
computing the total Sobol' index is a computationally expensive task for expensive-to-evaluate 
models with large number of uncertain parameters. Fortunately, 
for parameters with continuous distributions, an upper bound on $\mathcal{T}_i$  
can be expressed in terms of $\mu_i$ as follows: 
\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)},
%~(\propto \widehat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee
where $\mathcal{C}_i$ is the corresponding ``Poincar\'e constant''
and
$\mathbb{V}(\GG)$ is the total variance of the model
output~\cite{Lamboni:2013}.  The upper bound in the above inequality is
proportional to the product of $\mathcal{C}_i$ and $\mu_i$.  For the purpose of
parameter screening as discussed later in Section~\ref{sec:method}, we consider
a normalized product, $\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies
between 0 and 1:
\be
\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}.
\label{eq:cmu}
\ee
The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability
distribution of $\theta_i$. For $\theta_i \sim \mathcal{U}[a, b]$,
$\mathcal{C}_i = (b-a)^{2}/\pi^2$, and for  
$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$. 
Here $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with mean $\mu$
and variance $\sigma^2$, and $\mathcal{U}[a,b]$ denotes a uniform distribution
on the interval $[a, b]$.

>>>>

Derivative-based global sensitivity analysis is performed by 
computing derivative based global sensitivity measures (DGSMs)~\cite{Sobol:2009} 
for each uncertain parameter in the model. 
Specifically, we consider the following DGSMs, 
\be
\mu_i = 
\mathbb{E}\left[\left(\frac{\partial \GG(\bm{\bm{\theta}})}{\partial \theta_i}\right)^{2}\right], \quad i = 1, \ldots, \Np.
\label{eq:mu}
\ee
Here $\mathbb{E}$ denotes expectation over the uncertain parameters.
Notice that this formulation assumes that the function $\GG$ is differentiable
with respect to $\theta_i$, $i = 1, \ldots, \Np$ and the partial derivatives,
$\left(\frac{\partial \GG(\bm{\bm{\theta}})}{\partial \theta_i}\right)$ are 
square integrable.

@@

Consider the total 
Sobol' sensitivity index~\cite{Sobol:2001},
\be
\mathcal{T}(\theta_i) = 1 - 
\frac{\mathbb{V}[\mathbb{E}(\GG|\bm{\theta}_{\sim i})]}{\mathbb{V}(\GG)},
\label{eq:total}
\ee
where $\bm{\theta}_{\sim i}$ is the random vector $\bm\theta$ with $i$th component removed, 
and $\mathbb{V}$ denotes the variance. The total Sobol' index quantifies the total contribution 
of $\theta_i$ to variance of the model $\GG$. Components of $\bm\theta$ with small 
total Sobol' index can be considered inessential and can be fixed at nominal values. However, 
computing the total Sobol' index is a computationally expensive task for expensive-to-evaluate 
models with large number of uncertain parameters. Fortunately, 
for parameters with continuous distributions, an upper bound on $\mathcal{T}_i$  
can be expressed in terms of $\mu_i$ as follows: 
\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)},
%~(\propto \widehat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee
where $\mathcal{C}_i$ is the corresponding ``Poincar\'e constant''
and
$\mathbb{V}(\GG)$ is the total variance of the model
output~\cite{Lamboni:2013}.  The upper bound in the above inequality is
proportional to the product of $\mathcal{C}_i$ and $\mu_i$.  For the purpose of
parameter screening as discussed later in Section~\ref{sec:method}, we consider
a normalized product, $\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies
between 0 and 1:
\be
\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}.
\label{eq:cmu}
\ee
The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability
distribution of $\theta_i$. For $\theta_i \sim \mathcal{U}[a, b]$,
$\mathcal{C}_i = (b-a)^{2}/\pi^2$, and for  
$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$
(see~\cite{Lamboni:2013} for more details). 
Here $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with mean $\mu$
and variance $\sigma^2$, and $\mathcal{U}[a,b]$ denotes a uniform distribution
on the interval $[a, b]$.

### 2018-12-10 Paper/revision/source_files/disc.tex
..

In this work, we have presented an efficient and practical approach for constructing
a reduced-space
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the QoI. These parameters deemed as \textit{unimportant} are determined
using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
measures. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. These
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, RSS and FSS are
constructed using regression-based sparse PCEs. \rebut{Note however that the FSS is
constructed in an independent manner to ensure that the computational effort associated
with the proposed methodology does not overshoot the effort required to construct the 
FSS directly. Therefore, it does not impact the accuracy of the RSS which is only
constructed in situations where computational gains are expected.}

Parameter screening methodology was implemented to low-to-moderate dimensional
test problems and an accurate RSS was constructed to demonstrate potential for
computational gains in each case. Furthermore, the overall framework was
implemented  to a relatively higher dimensional application involving kinetics
of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
dimensions to 3 or 4 dimensions) was
accomplished for two different scenarios involving a fuel-rich and a fuel-lean
mixture. In both cases, the resulting RSS was able to capture the input-output
relationship as well as the uncertainty in the QoI with
reasonable accuracy. \rebut{Moreover, it was shown that the parameter
screening procedure (Algorithm~\ref{alg:screen}) was able to determine the
relative importance of the
parameters using only 5 samples in an even higher dimensional
case involving 33 uncertain rate-controlling parameters. It was observed that
the parameter dimension could be reduced from 33 to 2 in this case.}
Additional highlights of the proposed framework are as follows:
\begin{enumerate}
\item Although PCEs were used in this work, the proposed framework is
agnostic to the choice of the surrogate model construction method.
%\item The quantity of interest must be differentiable with respect to each uncertain parameter
%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving
compute-intensive simulations even if the scope for dimension reduction is
small. \rebut{However, computational gains using the proposed framework
are expected to increase significantly with the increase in dimensionality of the
parameter space.}
%Hence, careful judgment pertaining to the construction of a reduced-order
%surrogate as well as resource allocation is needed. is required when
%implementing the framework.

@@

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its potential for
identifying the unimportant model inputs. \rebut{In fact, in the numerical
tests and the chemical kinetics application presented in this work, reasonable
estimates of the screening metric are obtained during the initial screening
step with a few samples. This is indicative of a small degree of variability in
the gradient of the model output with respect to individual parameters, and
therefore, a low variance of the Monte Carlo estimator.} These observations
could be exploited to construct efficient model surrogates in a reduced input
space.

While the proposed approach has attractive features, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the QoI is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
\rebut{Moreover, in the presence of severe non-linearity in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. 
Also, we note that the proposed methodology aims to reduce the computational
effort pertaining to the total-effect Sobol' index, which is a
variance-based measure.  For severely nonlinear models, whose QoIs
might exhibit heavy-tailed or multimodal distributions, the 
variance might not provide an adequate representation of uncertainty.
Possible remedies for such cases include the so-called moment independent
measures; see e.g.,~\cite{BorgonovoIooss16,IoossLemaitre15}.}
%In the case of rare events, the variance-based methods typically
%lead to inaccurate estimates of the uncertainty in the model output. Since the
%methodology proposed in this work is based on reducing computational
%effort associated with variance-based sensitivity analysis, specifically, the
%total-effect Sobol' index, it might lead to erroneous estimates of the
%screening metrics and consequently the relative importance of the
%uncertain parameters.

>>>>

In this work, we have presented an efficient and practical approach for constructing
a reduced-space
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the QoI. These parameters deemed as \textit{unimportant} are determined
using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
measures. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. These
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, RSS and FSS are
constructed using regression-based sparse PCEs. Note however that the FSS is
constructed in an independent manner to ensure that the computational effort associated
with the proposed methodology does not overshoot the effort required to construct the 
FSS directly. Therefore, it does not impact the accuracy of the RSS which is only
constructed in situations where computational gains are expected.

Parameter screening methodology was implemented to low-to-moderate dimensional
test problems and an accurate RSS was constructed to demonstrate potential for
computational gains in each case. Furthermore, the overall framework was
implemented  to a relatively higher dimensional application involving kinetics
of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
dimensions to 3 or 4 dimensions) was
accomplished for two different scenarios involving a fuel-rich and a fuel-lean
mixture. In both cases, the resulting RSS was able to capture the input-output
relationship as well as the uncertainty in the QoI with
reasonable accuracy. Moreover, it was shown that the parameter
screening procedure (Algorithm~\ref{alg:screen}) was able to determine the
relative importance of the
parameters using only 5 samples in an even higher dimensional
case involving 33 uncertain rate-controlling parameters. It was observed that
the parameter dimension could be reduced from 33 to 2 in this case.
Additional highlights of the proposed framework are as follows:
\begin{enumerate}
\item Although PCEs were used in this work, the proposed framework is
agnostic to the choice of the surrogate model construction method.
%\item The quantity of interest must be differentiable with respect to each uncertain parameter
%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving
compute-intensive simulations even if the scope for dimension reduction is
small. However, computational gains using the proposed framework
are expected to increase significantly with the increase in dimensionality of the
parameter space.
%Hence, careful judgment pertaining to the construction of a reduced-order
%surrogate as well as resource allocation is needed. is required when
%implementing the framework.

@@

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its potential for
identifying the unimportant model inputs. In fact, in the numerical
tests and the chemical kinetics application presented in this work, reasonable
estimates of the screening metric are obtained during the initial screening
step with a few samples. This is indicative of a small degree of variability in
the gradient of the model output with respect to individual parameters, and
therefore, a low variance of the Monte Carlo estimator. These observations
could be exploited to construct efficient model surrogates in a reduced input
space.

While the proposed approach has attractive features, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the QoI is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
Moreover, in the presence of severe non-linearity in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. 
Also, we note that the proposed methodology aims to reduce the computational
effort pertaining to the total-effect Sobol' index, which is a
variance-based measure.  For severely nonlinear models, whose QoIs
might exhibit heavy-tailed or multimodal distributions, the 
variance might not provide an adequate representation of uncertainty.
Possible remedies for such cases include the so-called moment independent
measures; see e.g.,~\cite{BorgonovoIooss16,IoossLemaitre15}.
%In the case of rare events, the variance-based methods typically
%lead to inaccurate estimates of the uncertainty in the model output. Since the
%methodology proposed in this work is based on reducing computational
%effort associated with variance-based sensitivity analysis, specifically, the
%total-effect Sobol' index, it might lead to erroneous estimates of the
%screening metrics and consequently the relative importance of the
%uncertain parameters.

### 2018-12-10 Paper/revision/source_files/examples.tex
..

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/sense_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_borehole}
  \\ (a) & (b)
  \end{tabular}
  \\
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_borehole2}
  \\ (c)
\caption{
(a) Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain
parameters in the
borehole discharge function in~\eqref{eq:bore}; (b)
Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of
$\mathcal{T}(\theta_i)$ in each case in the legend; \rebut{and (c) Estimates of
$\widehat{\mathcal{C}_i\mu_i}$ for individual parameters using $N$ = 5, 10,
15, and 20 samples in the full parameter space.}}
\label{fig:sense_bore}
\end{center}
\end{figure}

In Figure~\ref{fig:sense_bore}(b), we plot estimates of the screening parameter 
$\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
samples used for approximating $\mu_i$ using~\eqref{eq:mu}. \rebut{Additionally,
to illustrate a comparison of the estimates of $\widehat{\mathcal{C}_i\mu_i}$ obtained
at the end of the initial screening step, i.e. $N$~=~5, with subsequent steps, we plot
them for individual parameters at $N$~=`5, 10, 15, and 20 samples in Figure~\ref{fig:sense_bore}(c).}
Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement
with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent 
with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear 
that the discharge is insensitive to $T_u$ and $T_l$. 
Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
the dimensionality of the problem: we can 
discount the variabilities in $T_u$, $T_l$, and $K_w$ by fixing 
them at their respective nominal values.

@@

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
  \\ (a) & (b)
  \end{tabular}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
  \\ (c)
\caption{(a) A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
the PCE constructed using 50 training points was found to be 
3, 2,and 2 in the 4D, 5D, and 7D case respectively;
(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
for the PCEs constructed in 4D, 5D, and 7D};
and (c) A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}
%
As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
clearly demonstrates the trade-off between
computational effort associated with surrogate construction and its predictive 
accuracy. For a small sample size of 20, the relative  error in the case of 4D
PCE is found to be the smallest. However, as the sample size increases, the higher
order PCE becomes more accurate. This is expected since the higher order PCE
inherently contains more information pertaining to the input-output relationship.
Note that the same set of 50 samples in the
validation test suite were used in each case. Hence, when limited computational resources
are available, the proposed methodology could yield substantial gains due to fast
convergence as well as higher accuracy of the surrogate in the reduced space.
The gains are expected to increase significantly as the dimensionality of the 
input space increases.}

@@

characteristics. \rebut{The degree of

@@

is plotted using the full-surrogate and the reduced-space PC surrogate.}

@@

\rebut{The comparison of predictive accuracy of the PCEs using $\epsilon_{\mbox{\tiny{L-2}}}$

@@

the proposed methodology significantly reduces computational effort in this case.}

>>>>

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/sense_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_borehole}
  \\ (a) & (b)
  \end{tabular}
  \\
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_borehole2}
  \\ (c)
\caption{
(a) Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain
parameters in the
borehole discharge function in~\eqref{eq:bore}; (b)
Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of
$\mathcal{T}(\theta_i)$ in each case in the legend; and (c) Estimates of
$\widehat{\mathcal{C}_i\mu_i}$ for individual parameters using $N$ = 5, 10,
15, and 20 samples in the full parameter space.}
\label{fig:sense_bore}
\end{center}
\end{figure}

In Figure~\ref{fig:sense_bore}(b), we plot estimates of the screening parameter 
$\widehat{\mathcal{C}_i\mu_i}$ for a wide range of the number of 
samples used for approximating $\mu_i$ using~\eqref{eq:mu}. Additionally,
to illustrate a comparison of the estimates of $\widehat{\mathcal{C}_i\mu_i}$ obtained
at the end of the initial screening step, i.e. $N$~=~5, with subsequent steps, we plot
them for individual parameters at $N$~=`5, 10, 15, and 20 samples in Figure~\ref{fig:sense_bore}(c).
Estimates for $\widehat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement
with $\mathcal{T}(\theta_i)$ even when small number of samples (5--10) are used. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent 
with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear 
that the discharge is insensitive to $T_u$ and $T_l$. 
Moreover, the sensitivity to $K_w$ is also small. We exploit these findings to reduce
the dimensionality of the problem: we can 
discount the variabilities in $T_u$, $T_l$, and $K_w$ by fixing 
them at their respective nominal values.

@@

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
  \\ (a) & (b)
  \end{tabular}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
  \\ (c)
\caption{(a) A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. The degree of
the PCE constructed using 50 training points was found to be 
3, 2,and 2 in the 4D, 5D, and 7D case respectively;
(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
for the PCEs constructed in 4D, 5D, and 7D;
and (c) A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}
%
As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
clearly demonstrates the trade-off between
computational effort associated with surrogate construction and its predictive 
accuracy. For a small sample size of 20, the relative  error in the case of 4D
PCE is found to be the smallest. However, as the sample size increases, the higher
order PCE becomes more accurate. This is expected since the higher order PCE
inherently contains more information pertaining to the input-output relationship.
Note that the same set of 50 samples in the
validation test suite were used in each case. Hence, when limited computational resources
are available, the proposed methodology could yield substantial gains due to fast
convergence as well as higher accuracy of the surrogate in the reduced space.
The gains are expected to increase significantly as the dimensionality of the 
input space increases.

@@

characteristics. The degree of

@@

is plotted using the full-surrogate and the reduced-space PC surrogate.

@@

The comparison of predictive accuracy of the PCEs using $\epsilon_{\mbox{\tiny{L-2}}}$

@@

the proposed methodology significantly reduces computational effort in this case.
